Distinguishing NFW and Isothermal Density Profiles with Weak Gravitational Lensing

### 2018-05-07 paper.tex
New figures

\documentclass[10pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\usepackage{microtype}
\usepackage{natbib}
\usepackage{graphicx}
% \usepackage{txfonts}

@@

Two commonly used density profiles in weak gravitational lensing are the isothermal profile and the Navarro-Frenk-White (NFW) profile.
We start with introducing the general characteristics of spherical density profiles, followed by cored isothermal and NFW profiles.
We then describe the purpose of our project, to distinguish between NFW and isothermal profiles, in detail.

@@

Tangential shear, along with the components of shear are shown as follows.
\begin{equation}
\gamma_t(\theta) = \overline{\kappa}(\theta) - \kappa(\theta)
\end{equation}

\begin{equation}
\gamma_1 = -\gamma_t \cos{2\phi}
\gamma_2 = -\gamma_t \sin{2\phi}
\end{equation}

It can be shown that for a spherical lens profile, the only component of shear should be the tangential shear, $\gamma_t$:
\citep{Dodelson2017}
\begin{equation}
\gamma = \gamma_t = \sqrt{{\gamma_1}^2 + {\gamma_2}^2} = -\gamma_1 \cos{2\phi} -\gamma_2 \sin{2\phi}
\end{equation}

@@

Prove that spherical density profiles only have tangential shear and ellipticity

@@

@@

@@

\subsection{Project Purpose}
The goal of this project is to devise a method to analyze lensed galaxy cluster data and find which density profile is more probable between the isothermal and NFW profiles.
In order to do so, we generate simulated data sets and analyze them to find the more probable profiles they would fit into.
This analysis method is expected to be usable in determining the characteristics of real observed data as well.

\newpage

@@

@@

\subsection{Questions}
\begin{itemize}
    \item How to properly do sigma contours?
    \item What theta range should we look at? (5 arcminutes?)
    \item What redshift is $\rho_\mathrm{crit}$ evaluated at? - at halo redshift - can we use current time?
    \item Using $c = 10$?
    \item Where to go from here?
\end{itemize}

@@

>>>>

\documentclass[10pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\usepackage{microtype}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{amsmath}
% \usepackage{txfonts}

@@

Two commonly used density profiles in weak gravitational lensing are the isothermal profile and the Navarro-Frenk-White (NFW) profile.
We start with introducing the general characteristics of spherical density profiles, followed by cored isothermal and NFW profiles.
We then describe the purpose of our project, to distinguish between NFW and isothermal profiles, in detail.
The goal of this project is to devise a method to analyze lensed galaxy cluster data and find which density profile is more probable between the isothermal and NFW profiles.
In order to do so, we generate simulated data sets and analyze them to find the more probable profiles they would fit into.
This analysis method is expected to be usable in determining the characteristics of real observed data as well.

@@

Strong lensing features take over when the convergence is greater than one.
Tangential shear, along with the components of shear are shown as follows.
\begin{equation}
\gamma_t(\theta) = \overline{\kappa}(\theta) - \kappa(\theta)
\end{equation}

The tangential shear is decomposed into two components, $\gamma_1$ and $\gamma_2$. $\gamma_1$ represents stretching along the $\theta_x$ and $\theta_y$ axes, and $\gamma_2$
\begin{equation}
\begin{split}
\gamma_1 = -\gamma_t \cos{2\phi}\\
\gamma_2 = -\gamma_t \sin{2\phi}
\end{split}
\end{equation}

It can be shown that for a spherical lens profile, the only component of shear $\gamma$ should be the tangential shear, $\gamma_t$:
\citep{Dodelson2017}
\begin{equation}
\gamma = \gamma_t = \sqrt{{\gamma_1}^2 + {\gamma_2}^2} = -\gamma_1 \cos{2\phi} -\gamma_2 \sin{2\phi}
\end{equation}

@@

@@

\begin{figure}
    \includegraphics{isothermalproperties.pdf}
    \caption{Lensing quantities for a CIS profile with $M_{200} = 10^{15} M_\odot$ and $r_c = 10$ kpc.}
    \label{}
\end{figure}

@@

What redshift is $\rho_\mathrm{crit}$ evaluated at? - at halo redshift - can we use current time?

@@

\begin{figure}
    \includegraphics{nfwproperties.pdf}
    \caption{Lensing quantities for a NFW profile with $M_{200} = 10^{15} M_\odot$ and $c = 10$.}
    \label{}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=0.49\textwidth]{isothermalellipticities.pdf}
    \includegraphics[width=0.49\textwidth]{nfwellipticities.pdf}
    \caption{plots}
    \label{}
\end{figure}

@@

What theta range should we look at? (5 arcminutes?)

How to properly do sigma contours?

@@

Where to go from here?
